The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
Spellcheck

The study was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hyptheses and to formulate clear research questions. This was achieved by using a data-driven approach to analysing the code and documentation. The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phsae. Both phases were performed iteratively. This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.

@@

\smallskip \noindent
\textbf{Corrective  }
%Define what kinds of changes these are
Corrective changes are identified as types of change that fix broken functionality.
%Data and explanation
No corrective changes were identified between v1.4 and v2.0. There are two main reasons that we did not find any changes of this type. Firstly, the majority of changes were additions or re-implementations of functionality. This meant that most of the existing code was either removed, replaced or deprecated, resulting in little to no obvious fixes. Secondly, we only had access to the public facing API and not the implementation itself. We therefore could not inspect the inner workings of the functionality that has remained between versions to determine if any corrective change took place.
%Conclusion
We therefore conclude that the evolution of the API was not driven by corrective changes.

@@

\smallskip \noindent
\textbf{Preventive  }
%Define
Preventive changes are defined to be changes that attempt to avoid future maintenance. This should not be confused with changes that attempt to make the current state of the system more maintainable.
%Data and examples
Two changes were identified to be preventive types of change. A new error handling system was one of these changes. Version 2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API. The redesign of the system to make use of interfaces was also classified as a preventive change. Using interfaces to access modules helps to make them more maintainable and more easily extendable.
%Concusion
Preventive types of change appear to drive the evolution of an API more strongly than other types of change. This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.

@@

\smallskip \noindent
\textbf{Reformative  }
%Define
Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
%Data and Example
One reformative change was identified between v1.4 and v2.0; a redesign of the existing example programs. The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.
%Conclusion
We therefore conclude that reformative changes, while important for the usability of the API, do not drive the evolution of the API.

>>>>

The study was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hypotheses and to formulate clear research questions. This was achieved by using a data-driven approach to analysing the code and documentation. The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase. Both phases were performed iteratively. This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.

@@

\smallskip \noindent
\textbf{Corrective  }
%Define what kinds of changes these are
Corrective changes are identified as types of change that fix broken functionality.
%Data and explanation
No corrective changes were identified between version 1.4 and version 2.0. There are two main reasons that we did not find any changes of this type. Firstly, the majority of changes were additions or re-implementations of functionality. This meant that most of the existing code was either removed, replaced or deprecated, resulting in little to no obvious fixes. Secondly, we only had access to the public facing API and not the implementation itself. We therefore could not inspect the inner workings of the functionality that has remained between versions to determine if any corrective change took place.
%Conclusion
We therefore conclude that the evolution of the API was not driven by corrective changes.

@@

\smallskip \noindent
\textbf{Preventive  }
%Define
Preventive changes are defined to be changes that attempt to avoid future maintenance. This should not be confused with changes that attempt to make the current state of the system more maintainable.
%Data and examples
Two changes were identified to be preventive types of change. A new error handling system was one of these changes. Version 2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API. The redesign of the system to make use of interfaces was also classified as a preventive change. Using interfaces to access modules helps to make them more maintainable and more easily extensible.
%Concusion
Preventive types of change appear to drive the evolution of an API more strongly than other types of change. This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.

@@

\smallskip \noindent
\textbf{Reformative  }
%Define
Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
%Data and Example
One reformative change was identified between version 1.4 and version 2.0; a redesign of the existing example programs. The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.
%Conclusion
We therefore conclude that reformative changes, while important for the usability of the API, do not drive the evolution of the API.
